\chapter{又有一个内容}
\begin{paracol}{2}[]

今天全沒月光，我知道不妙。早上小心出門，趙貴翁的眼色便怪：似乎怕我，似乎想害我。還有七八個人，交頭
接耳的議論我，又怕我看見。一路上的人，都是如此。其中最兇的一個人，張着嘴，對我笑了一笑；我便從頭直
冷到腳跟，曉得他們布置，都已妥當了。

\switchcolumn

Today, there was no moonlight whatsoever. I know that can't be good. I was careful when I went out
this morning. Zhao Guiweng gave me a strange look, as if he was both afraid of me and also wanted
to do me in. There were also another seven or eight people discussing me in hushed tones, hoping
that I wouldn't see them. Everybody that I encountered along my route was like this. Among them,
the most intimidating was a person who gave me an open-mouthed smile; it sent a chill from my head
straight to my toes. I knew at that moment that their plans for me were already set.

\switchcolumn*

我可不怕，仍舊走我的路。前面一夥小孩子，也在那裏議論我；眼色也同趙貴翁一樣，臉色也都鐵青。我想我同
小孩子有什麼讎，他也這樣。忍不住大聲說，「你告訴我！」他們可就跑了。

\switchcolumn

I couldn't show fear, so I just continued along my original route. There was a group of children
ahead of me that were also discussing me. They gave me the same look that Zhao Guiweng had given
me. Their eyes were filled with rage. I tried to think what possible enmity I might have with these
children that they might behave in such a way. I couldn't help but yelling out, ``Tell me!'' They
ran off.

\switchcolumn*

我想：我同趙貴翁有什麼讎，同路上的人又有什麼讎；只有廿年以前，把古久先生的陳年流水簿子，踹了一腳，
古久先生很不高興。趙貴翁雖然不認識他，一定也聽到風聲，代抱不平；約定路上的人，同我作寃對。但是小孩
子呢？那時候，他們還沒有出世，何以今天也睜着怪眼睛，似乎怕我，似乎想害我。這眞教我怕，教我納罕而且
傷心。

\switchcolumn

I tried to think what possible enmity I might have with Zhao Guiweng or with the others along my
route. The only thing that came to mind was when I had stepped on Mr.\ Gu Jiu's account ledger
twenty years ago. It was quite old. Mr.\ Gu Jiu was not happy when I did that. Even though Zhao
Guiweng doesn't know him, he certainly must have heard something. Perhaps that's why he's mad at
me. Maybe he turned the others along my route against me. But what about the children? They weren't
yet born when that happened. Why would they give me such strange looks now, as if they both feared
me and wanted to do me in. This caused me to be truly afraid. It also took me aback and hurt my
feelings.

\switchcolumn*

我明白了。這是他們娘老子教的！

\switchcolumn

I understand. Their parents are making them act like this!

\end{paracol}